Scheduling and Amortization for MPC

### 2022-01-12 paper_SIMD.tex
Commented out incorrect handling of targetless phi nodes. Added a TODO in Extension to Basic Vectorization.

\ana{TODO: We need to remove phi-nodes that end up without incoming back-edges.}

The final step is to remove array phi-nodes that are left without incoming back edges after removal of infeasible edges.
Clearly, such a phi-node is redundant when there are no loop-carried dependences that are due to writes to the corresponding array.
In our running example, the phi-nodes for \texttt{A}, \texttt{B}, and \texttt{C}, are all redundant.

Removing redundant phi-nodes is as follows.
Denote a redundant phi-node by $\texttt{A}_1 = \phi(\texttt{A}_0,\texttt{A}_k)$. $\texttt{A}_0$ is the array at the beginning of the loop
and $\texttt{A}_k$ is the array at the end of an iteration (including the last iteration). For each outer-to-inner or same-level def-use edge
that originates at the node, replace $\texttt{A}_1$ at the use node by $\texttt{A}_0$. This is correct, i.e., it is guaranteed that the use
references $\texttt{A}_0$; had the use been referencing an array modified in an earlier iteration, the back-edge to the phi-node would
not have been removed and the phi-node would not have been classified as redundant.
For each inner-to-outer def-use edge, replace $\texttt{A}_1$ by $\texttt{A}_k$. In this case, the use references the array
that results from the computation in the loop.

@@

@@

>>>>

\ana{Commented out previous writeup. Removal/handling of targetless phi-nodes will go into the Extension to Basic vectorization.}

\begin{comment}
The final step is to remove array phi-nodes that are left without incoming back edges after removal of infeasible edges.
Such a phi-node is redundant when there are no loop-carried dependences that are due to writes to the corresponding array.
In our running example, the phi-nodes for \texttt{A}, \texttt{B}, and \texttt{C}, are redundant.

Removing redundant phi-nodes proceeds from \emph{innermost to outermost} loops as follows.
Denote a redundant phi-node by $\texttt{A}_1 = \phi(\texttt{A}_0,\texttt{A}_k)$. $\texttt{A}_0$ is the array at the beginning of the loop
and $\texttt{A}_k$ is the array at the end of an iteration (including the last iteration). We consider two cases:
\begin{enumerate}
\item[Case 1] Inner-to-outer or same-level def-use edge
\begin{itemize}
\item If use is an array read $ ... = \texttt{A}_1[f(i)]$, then replace $\texttt{A}_1$ with $\texttt{A}_0$. This is correct, i.e., it is guaranteed that the use
references $\texttt{A}_0$; had the use been referencing an array modified in an earlier iteration, the back-edge to the phi-node would
not have been removed and the phi-node would not have been classified as redundant.
\item If use is an array write (update) $\texttt{A}_2 = \texttt{A}_1; \texttt{A}_2[i] = ... $ equiv. to $\texttt{A}_2 = \mathit{update}(\texttt{A}_1, i, ...)$ then handling becomes more tricky.
The semantics of this update is that when $i$ is 0, then $\texttt{A}_0$ is being read. But when $i > 0$, then $\texttt{A}_k$ is being read. If we are at this case, this means that the def-use edge is same-level and we are removing a redundant node in the loop enclosing the update. The removal of the original phi-node entails pushing the phi-node at the update:
$\texttt{A}_2 = \phi(\texttt{A}_0,\texttt{A}_k); \texttt{A}_2[i] = ... $ equiv. to $\texttt{A}_2 = \mathit{update}(\phi(\texttt{A}_0,\texttt{A}_k), i, ...)$.
\item If use is a phi-node $... = \phi(\texttt{A}_1,...)$, that means we have an outer-to-inner edge. The

\end{itemize}
\end{enumerate}
For each outer-to-inner or same-level def-use edge
that originates at the node, replace $\texttt{A}_1$ at the use node by $\texttt{A}_0$. 
For each inner-to-outer def-use edge, replace $\texttt{A}_1$ by $\texttt{A}_k$. In this case, the use references the array
that results from the computation in the loop.

@@

\begin{algorithmic}
\STATE for i in range(N):
\STATE 1. $\texttt{D}_0$ = $\phi(\texttt{D},\texttt{D}_1)$
\STATE 2. $\texttt{A}_1$ = $\texttt{A}$; $\texttt{A}_1$[i] = $\texttt{B}$[i] + 10;
\STATE 3. $\texttt{B}_1$ = $\texttt{B}$; $\texttt{B}_1$[i] = $\texttt{A}_1$[i] * $\texttt{D}_0$[i-1];
\STATE 4. $\texttt{C}_1$ = $\texttt{C}$; $\texttt{C}_1$[i] = $\texttt{A}_1$[i] * $\texttt{D}_0$[i-1];
\STATE 5. $\texttt{D}_1$ = $\texttt{D}_0$; $\texttt{D}_1$[i] = $\texttt{B}_1$[i] * $\texttt{C}_1$[i];
\end{algorithmic}
\end{comment}

@@

\ana{TODO: Handling of Targetless phi nodes should be done here, as an extension to Basic Vectorization.}
